A Formal Model of Checked C

### 2023-01-09 sandp23/formal.tex
Adding type checking

>>>>

\subsection{Type Checking}
\label{sec:typechecking}
Our type checker restricts the usage of tainted and checked pointer types to ensure that tainted pointers do not affect checked types, along with enforcing~\checkedc typing rules~\cite{li22checkedc}.
A few selected type rules are presented in~\fig{fig:type-system-1}.
The complete set of typing rules and special handling of (NT)-arrays are provided in~\apdx{sec:literal-pointer-typing}.

Each typing judgment has the form $\Gamma;\Theta\vdash_m e : \tau$,
which states that in a type environment $\Gamma$ (mapping variables to
their types) and a predicate environment $\Theta$ (mapping integer-typed
variables to Boolean predicates), expression $e$ will have type $\tau$ if evaluated
in context mode $m$.
